My Cool Title

### 2019-05-05 paper.tex
Changed picture caption
Adding abstract

\begin{abstract}
  Cool abstract here
  \keywords{Active vision, vision impairment, object detection}
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/control_loop_no_controller.png}
  \caption{A set of CDFs comparing the time to target. }\label{fig:sys-diagram-no-controller}
\end{figure}

@@

>>>>

\begin{abstract}
  The ActiVis project aims to deliver a system for a mobile device that is able to guide a person with visual impairments towards a target object or area in an unknown indoor environment. 
  To do so, it uses new developments in object detection methods, mobile computing and action generation. 
  \keywords{Active vision, vision impairment, object detection}
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\textwidth]{figures/control_loop_no_controller.png}
  \caption{The control loop with the human acting as bot manipulator and controller. }\label{fig:sys-diagram-no-controller}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\textwidth]{figures/environment.png}
  \caption{A picture of the experiment setup. }\label{fig:boxplot-time}
\end{figure}
